For our project we chose to measure and compare several ext4 filesystem parameters
in an operating system (OS) running directly on a machine (host) and in the same 
OS running on a virtual machine (VM) on top of the host OS. In addition to being an 
interesting study in the inner workings of the ext4 filesystem, this paper seeks to
elucidate the similarities and differences between host and virtual machine I/O in
terms of latency, and also reveal the way I/O is virtualized in a VM.

In particular, we determined the ideal buffer size for random I/O by preforming random reads
of varying sizes. Next, we reverse engineered prefetch size linux kernel uses to speed up
sequential reads by measuring sequential read latency. We were also interested in file cache size.
We measured throughput of repeated reads of a big file, which decreased substantially as soon
as the file was bigger than the cache. Finally, we were tried to determine file size that triggers 
file system to add a layer of indirection between inode and data blocks. By measuring one-byte
append latency to a file, we expected to see higher latency when an append causes file system
to write additional metadata for indirect pointer.

We found that the host and VM filesystem had similar characteristics across all measured parameters. For instance, the 
optimal size to randomly read a file was N*4KB, a multiple of the page size of the 
system, and that for large reads the best through put was achieved at approximately
7MB. The maximum prefetch size was 128KB for both the host and the VM. We also 
determined that the file cache size was related to the amount of physical memory 
available while our process was running. Finally, we proved that there is no single file
size after which ext4 adds another level of indirection in host environment. We couldn't prove
similar hypothesis on a virtual machine.

The rest of the paper is organized as follows. In Section~\ref{sec:method} we 
discuss our experimental setup and methodology for our experiments. In 
Section~\ref{sec:results} we discuss our experiments and results in detail. 
Finally, in Section~\ref{sec:conc} we summarize our findings and conclusions.

