% Timer, Platform
We ran our experiments on a Dell Precision T7500n Dual Processor desktop 
computer running 64-bit RHEL6 built on the 2.6.32 kernel for CentOS6. The 
machine housed a Dual Quad Core Intel\textsuperscript{\textregistered} 
Xeon\textsuperscript{\textregistered} E5620 2.40GHz Processor, 24GB of RAM, 
and two 600GB 15K RPM harddrives. Note, however, that during our experiments 
we restricted disk accesses to only one harddrive.

In order to perform our comparison with a virtual machine, we used VMware 
workstation to emulate a two-core machine running 32-bit RHEL6 built on the 
Linux 2.6.32 kernel for CentOS6 with 8GB of RAM and one 60GB virtual harddrive.

\subsection{Considerations}
There were several aspects that we considered in order to obtain our data, 
including our measurement technique, file system caching, noise, and validation.

\subsubsection{Timer}
For our measurements we used the \texttt{rdtsc} and \texttt{rdtscp} assembly instructions, which load 
the current timestamp counter value (in cycles) into the designated registers. In 
order to guarantee in-order execution of our instructions, we inserted the cpuid 
instruction ahead of \texttt{rdtsc} to get the timestamp value before the function we wanted 
to measure. We then used \texttt{rdtscp} to guarantee completion of the measured function 
before reading timestamp counter again. We used advices on measuring from Intel's white paper\cite{rdtsc}.

In order to verify the accuracy of our timer, we first compared the time measured 
using \texttt{rdtsc/rdtscp} with gettimeofday in the non-virtual environment. We calculated
the processor frequency for each measurement and found that the values from 
\texttt{rdtsc/rdtscp} and \texttt{gettimeofday} resulted in the correct value. We performed this 
same task on the VM and got the same result.

\subsubsection{Flushing and Clearing Buffer Cache}
The cache was an important factor in all of our tests. When running our tests on the
virtual machine we were careful to clear both the guest and the host caches using 
\texttt{drop\_caches} file in \texttt{/proc/sys/vm} when necessary. Since the VM runs as a process on the host, memory 
accessed by the VM are cached in the host as well. However, clearing the cache on the VM 
does not clear the cache of the host due to the principle of isolation. To deal with this
issue, we developed a simple server-client program in Python. Whenever we clear the cache on the VM
 we issue a message to the host through a certain port. A process on the host listens to this port and clears the cache on
receipt of the message.

\subsubsection{Test Files}
We used the following command to generate arbitrary sized files containing random
data from which to read, where outputFilePath is the path to the outputted file 
and numMB is the number of MB to generate.

\begin{verbatim}
dd if=/dev/urandom of="outputFilePath" 
   bs=1MB count=numMB
\end{verbatim}

\subsubsection{Noise}
During our experiments we encountered some amount of noise in our 
timing measurements. In order to address this, we used several techniques. First,
we collected data over repetitive runs. We also used the minimum instead of the average
over multiple runs for some experiments. We argue that this is a valid metric given 
that disk accesses experience a minimum latency due to the time to transfer data.
In our experiments we care mostly about the lower bound latency, and care less about 
variability due to other factors such as process getting descheduled or seek time. Also,
this helped us detect when some of the reads were served from the cache, since the minimum 
for that data point was suspiciously low. On other hand, it would only slightly affect the average,
which would be harder to detect.